Typed Clojure

### 2014-09-30 icfp15-typedclojure.tex
rename to icfp
type hints

@@

We currently do not support Java generics
% because generics don't "exist" on the JVM
% clojure also doesn't use them

>>>>

\infer [S-Instance]
{ \class{},\ \classp{}\ not\ arrays
\\ \assignable {\class{}} {\classp{}}}
{ \inpropenv {} {\issubtype {\Instance {\class{}}} {\Instance {\classp{}}}} }

@@

We do not support Java Generics for several reasons. Firstly
Clojure programmers already use \emph{type hints} to resolve
Java methods which does not interact with generics. Secondly
it would complicate the type system to need to consider advanced
Generics features like existentials and f-bounded polymorphism
which has complicated other type systems like Scala's.
Finally Java interop is rare in Clojure code, so the extra
work needed would not be worth the effort compared to the number
of new bugs core.typed catches.

Thanks to type erasure, only unparameterised classes, primitive
types and array classes live at runtime. This simplifies 
inference for \emph{tools.analyzer}, which uses type hints
to resolve ambiguities in Java interop like overloaded methods.

\subsection{Clojure type hints}

Clojure comes with a small type system that helps improve
performance in Clojure code: type hints. They are used to help
the compiler resolve Java methods and prevent unboxing in
certain situations. Tags are propagated bidirectionally
and the programmer is free to add them where they like.
